Proportional multi-state multiple-cohort life table model

### 2018-05-02 MSLT/MSLTdoc.Rmd
Tidy graph labels

require(dplyr)
require(tidyverse)
require(knitr)
require(kableExtra)
require(citr)
require(gridExtra)
require(cowplot)
require(ggpubr)

@@

23) Plot outcomes for each age and sex cohort using created functions. Two functions are used: plot_output (plots outputs) and grid_arrange_shared_legend (places one label per page).

```{r echo=TRUE}
## Do a loop, the first in_outcomes is age.

@@

            p_index  <- plot_output(in_data = output_df, in_age = age, in_population = sex, in_outcomes = c("age", paste(outcome, "num", "bl", disease, sep = "_"), paste(outcome, "num", "sc", disease, sep = "_"), paste(outcome, "num", "diff", disease, sep = "_")), in_disease = disease)

            # There are 4 diseases for males, this should be modified according to the modelled 
            # diseases.

@@

                pdf(paste0(output_dir, "/", paste(age, sex, outcome, sep="_"), ".pdf"))
                grid_arrange_shared_legend (p1, p2, p3, p4, ncol = 2, nrow = 2, mainTitle = paste(age, sex, outcome),mainLeft = 'Cases', mainBottom = 'Age')
                dev.off()

@@

            # There are 5 diseases for females, this should be modified according to the modelled 
            # diseases.

@@

                pdf(paste0(output_dir, "/", paste(age, sex, outcome, sep="_"), ".pdf"))
                grid_arrange_shared_legend (p1, p2, p3, p4, p5, ncol = 2, nrow = 3, mainTitle = paste(age, sex, outcome), mainLeft = 'Cases', mainBottom = 'Age')
                dev.off()

@@

>>>>

require(dplyr)
require(tidyverse)
require(knitr)
require(kableExtra)
require(citr)
require(gridExtra)
require(cowplot)
require(ggpubr)
require(grid)
require(ggplot2)

@@

23) Plot outcomes for each age and sex cohort using created functions. Founr functions are used: plot_output (plots outputs), grid_arrange_shared_legend and g_legend (places one label per page) and get_qualified_disease_name (replaces full name of disease)

```{r echo=TRUE}

@@

            p_index  <- plot_output(in_data = output_df, in_age = age, in_population = sex, in_outcomes = c("age", paste(outcome, "num", "bl", disease, sep = "_"), paste(outcome, "num", "sc", disease, sep = "_"), paste(outcome, "num", "diff", disease, sep = "_")), in_disease = get_qualified_disease_name(disease))

                      #                 paste0(if(disease == "ihd") {
                      # disease == "Ischemic heart disease"
                      # } else {
                      # if (disease == "istroke") {
                      # disease == "Ischemic stroke"
                      # } else {
                      # if (disease == "colon_cancer") {
                      # disease == "Colon cancer"
                      # } else {
                      # if (disease == "diabetes") {
                      # disease == "Diabetes"
                      # } else {
                      # if (disease == "breast_cancer") {
                      # disease == "Breast Cancer"}}}}}))

@@

                pdf(paste0(output_dir, "/", paste(age, sex, outcome, sep="_"), ".pdf"))
                grid_arrange_shared_legend (p1, p2, p3, p4, ncol = 2, nrow = 2, mainTitle = paste(ifelse(outcome == "mx", "Deaths", "Incidence"), sex, "cohort mid age", age),
                                          mainLeft = 'Cases', mainBottom = 'Age')
                dev.off()

@@

@@

                pdf(paste0(output_dir, "/", paste(age, sex, outcome, sep="_"), ".pdf"))
                grid_arrange_shared_legend (p1, p2, p3, p4, p5, ncol = 2, nrow = 3, mainTitle = paste(ifelse(outcome == "mx", "Deaths", "Incidence"), sex, "cohort mid age", age), mainLeft = 'Cases', mainBottom = 'Age')
                dev.off()

@@

## Insert the plots in the rmarkdown doc
